Beliefs about the development of mental life

### 2025-01-06 paper/paper_anonymized.Rmd
make anonymized versions

---
# title: "Beliefs about the development of mental life"
# author: 
#   - "Kara Weisman\\newline University of California, Riverside\\newline ORCID: https://orcid.org/0000-0002-3706-7554"
#   - "Lucy S. King\\newline Vanderbilt University\\newline ORCID: http://orcid.org/0000-0002-2552-0614"
#   - "Kathryn Humphreys\\newline Vanderbilt University\\newline ORCID: https://orcid.org/0000-0002-5715-6597"
# output:
#   pdf_document:  default
#   # word_document:
#     # reference_docx: word-styles-ref.docx
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover.tex
    toc: false
    number_sections: false
bibliography: ../supplement/references.bib
csl: ../supplement/apa.csl
figsintext: yes
header-includes:
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[5]
- \usepackage{float}
---

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce). All studies were approved by the Research Compliance Office, Human Subjects Panel (IRB) at Stanford University. For extended descriptions of methods and results, see Supplemental Materials.

@@

Participants completed three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years. On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs. These photographs (and all materials used in these studies) are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND). Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").

>>>>

---
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover_anonymized.tex
    toc: false
    number_sections: false
bibliography: ../supplement/references.bib
csl: ../supplement/apa.csl
figsintext: yes
header-includes:
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[5]
- \usepackage{float}
- \usepackage{url}
---

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}). All studies were approved by [IRB information omitted for anonymous review]. For extended descriptions of methods and results, see Supplemental Materials.

@@

Participants completed three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years. On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs. These photographs (and all materials used in these studies) are available in the following OSF repository: \url{https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52} (anonymized link for peer review). Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").

### 2025-01-06 supplement/supplement-main_anonymized.Rmd
make anonymized versions

---
# title: "Beliefs about the development of mental life"
# subtitle: "Supplemental Materials"
# author: "Kara Weisman, Lucy S. King, and Kathryn Humphreys"
# date: "2024-12-30"
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover.tex
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 2
    number_sections: false
  #   reference_docx: word-styles-ref.docx
  # word_document:
bibliography: "references.bib"
csl: apa.csl
# cls: article.cls
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \modulolinenumbers[5]
   - \usepackage{float}
   - \usepackage{pdflscape}
tables: yes
---

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).

All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).

All studies were approved by the Institution Review Board for Human Subjects at Stanford University.

>>>>

---
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
      before_body: cover_anonymized.tex
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 2
    number_sections: false
  #   reference_docx: word-styles-ref.docx
  # word_document:
bibliography: "references.bib"
csl: apa.csl
# cls: article.cls
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \modulolinenumbers[5]
   - \usepackage{float}
   - \usepackage{url}
   - \usepackage{pdflscape}
tables: yes
---

@@

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.

@@

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}).

All materials used in these studies are available in the following OSF repository: \url{https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52} (anonymized link for peer review).

All studies were approved by [IRB information omitted for anonymous review].
